### 2021-04-20 README.Rmd
Further development needed to implement the inclusion of NumNe and midyexpB into zoneD and its derivatives. These are the pre-fishing numbers and expoitable biomass.

* 2021-04-19 0.0.0.3000 Started development required to generalize the use of the doprojection function (it was previously called doTASprojection). This generalization requires the generation of separate functions to process the data for cpue, any FIS, and the numbers-at-size. Numerous diganostic plots have been added, also providing a template for adding more  (see News.md for history of development).

@@

indata <- list(arrce=condC$histCE,yearnames=rownames(condC$histCE),
               acatches=tail(condC$histCatch,1),fis=NA,nas=NA)
cmcda <- mcdahcr(indata,hsargs=hsargs,saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

>>>>

* 2021-04-20 0.0.0.2900 Continuing process of modifying the core functions to allow for the numbers-at-size prior to fishing and the midyear-exploitB (midyexpB) to be included in teh zoneD object. doprojection still requires fursther modification to account for applying to chosen HCR and HS to the completed conditioned zoneDD to provide the first year of expected catches in the projections (which are to be defined by teh conditoned data prior to projections beginning).

@@

#explicit definition of indata rather than using the tasdata function
indata <- list(arrce=condC$histCE,yearnames=rownames(condC$histCE),
               acatches=tail(condC$histCatch,1),fis=NULL,nas=NULL)
cmcda <- mcdahcr(indata,hsargs=hsargs,saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojection(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
# prepareprojection needs to be modified so that is uses expected catches rather
# than calculating them internally (which will differ by jurisdiction)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR
